---
title: "Connections"
author: "Jayant"
date: "2/22/2020"
output: pdf_document
---

# Different functions

**file** opens a connection with a standard uncompressed file 

**gzfile** opens a connection with a file compressed with gzip

**bzfile** opens a connection with a file compressed with bzip2

**url** opens a connection with a web-page

**str()** is a compact way to display the structure of an R object.

# file Function

```{r}
str(file)
```

description -> Name of the file

open -> which mode i.e. :- 

                           r -> read only       ;       rb -> read in binary 
                           
                           w -> New file write  ;       wb -> write in binary
                           
                           a -> appending       ;       ab -> append in binary

Connections can be used to read parts of a file :_

***Code:-***
con <- gzfile("words.gz")
x <- readLines(con,10)
x

***Oputput:-***
[1] "1080"      "10-point"  "10th"  "11-point"
[2] "12-point"  "16-point"  "18th"  "1st"
[3] "2"         "20-point"

writeLines() takes a character vector and writes each element one line at a time to a text file. 

# url Function

```{r}
con <- url("http://www.jhsph.edu","r")
x <- readLines(con)
head(x)
```