---
title: "Data Output"
author: "Jayant"
date: "2/21/2020"
output: pdf_document
---
DPUT or DUMP give output with meta data in text format which is more useful than the others :-

1. write.table

2. writeLines

3. save

4. serialize

Meta data helps when retieving data from the file and helps avoid loss of data.

# DPUT
```{r}
y <- data.frame(a = 1 , b = "a")
dput(y,file="y.R")

new.y <- dget("y.R")
new.y
```
**O/P of dput (including meta data)**

Structure(  list(  a = 1, 

                   b = structure(1L, .Label = "a",
                   
                                 class = "factor")
                                 
                                )
                                
          ,  class = "data.frame", row.names = c(NA, -1L) 
          
         )
         
DGET can only be used on one R object.

# DUMP
Dump can be used on multiple R objects
```{r}
x <- "foo"
y <- data.frame(a = 1 , b = "a")
dump(c("x","y"),file = "data.R")
rm(x,y)                         #Removing x and y will work without this.
source("data.R")
y
x
```